### 2013-09-26 Tex/chapters/results.tex
Neue, bessere Bootstrap Methode zur Fehlerfindung

    The bootstrap method estimates the error \(\Delta \overline{\avg{O}}\)
    by taking \(M\) random samples from the \(M\) measurements of \(O\),
    where the same measurement can be chosen more than once, calculating the
    estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
    times. Then the standard deviation of the \(k\) calculated \(\avg{O_b}\)
    is taken as an estimate for \(\Delta \overline{\avg{O}}\).
    In this thesis the number of bootstrap samples is \(k = 200\).\\
    Note that the error of \(\avg{O}\), which is the standard error\footnote{for the arthmetic mean: standard deviation divided by \(\sqrt M\), where \(M\) is the number of samples}
    of different states on one instance of a proximity graph \(\Delta \avg{O}\),
    is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}.
    However \(\Delta \overline{\avg{O}}\), which is the the error of the
    observable averaged over different instances of the proximity graphs,
    is not dependend on \(\tau\), because different realizations of the
    random proximity graph are surely uncorrelated.
    Because every error mentioned in this thesis is of this type, it is not
    necessary to determine \(\tau\) for each observable. Therefore a good
    error estimate can be achieved by simple bootstrapping. Nevertheless, one has
    to simulate enough uncorrelated states for each realization to keep
    the \(\Delta \overline{\avg{O}}\) small. For every determined value an

>>>>

    There are two kinds of errors in this simulations. On the one hand
    there are thermal fluctuations in the simulation of one graph realization and
    on the other hand there are fluctuations in the structure of the realizations.
    To account for both, first a resampling of the "timeline" of one
    realization is performed. From these resamples the expected values of
    the observables \(\avg\abs{m}, \chi\) and \(g\) are estimated for each
    realization. Those are then resampled and from the resampled values
    one bootstrap average \(\avg{O}b\) is calculated. This procedure is
    repeated until 20 different bootstrap averages are present. Their
    mean and standard deviation are the used as \(\overline{\avg{O}}\) and
    its standard error \(\Delta \overline{\avg{O}}\). A shematic figure of
    this is shown in Fig.\ \ref{fig:bootstrap}.
    % TODO
    For every determined value an
